### 2023-11-06 manuscript/manuscript.Rmd
Update the assignment assessments section of the methods to include the standards mix data

Features matching to possible ionisation products of the spiked urine compounds were identified by first applying the MZedDB ionisation 'rules' and calculating their theoretical *m/z* for each of the adducts specified in Section \@ref(relationships) [@draper2009].
The calculated *m/z* were then matched to the spiked urine features using a search range of $\pm$ `r search_ppm` ppm.

>>>>

Features matching to possible ionisation products of the chemical standards were identified by first applying the MZedDB ionisation 'rules' and calculating their theoretical *m/z* for each of the adducts specified in Section \@ref(relationships) [@draper2009].
The calculated *m/z* were then matched to the *m/z* features in the standards mix and spiked urine data using a search range of $\pm$ `r search_ppm` ppm.
